Functional vs. Object Oriented Programming: Productivity comparison

### 2015-10-25 article.tex
some fixing

\begin{itemize}
\item FASTA, generate and write random DNA sequences
\item k-nucleotide, repeatedly update hashtables and k-nucleotide strings
\item Mandelbrot, generate a Mandelbrot set and write a portable bitmap
\item n-body, perform an N-body simulation of the Jovian planets
\item pi-digits, calculate the digits of Pi with arbitrary-precision arithmetic
\item regex-dna, match DNA 8-mers and substitute nucleotides for IUB code
\item reverse-complement, read DNA sequences and write their reverse-complement
\item spectral-norm, calculate an eigenvalue using the power method
\end{itemize}

>>>>

\begin{itemize}
\item FASTA, generate and write random DNA sequences.
\item k-nucleotide, repeatedly update hashtables and k-nucleotide strings.
\item Mandelbrot, generate a Mandelbrot set and write a portable bitmap.
\item n-body, perform an N-body simulation of the Jovian planets.
\item pi-digits, calculate the digits of Pi with arbitrary-precision arithmetic.
\item regex-dna, match DNA 8-mers and substitute nucleotides for IUB code.
\item reverse-complement, read DNA sequences and write their reverse-complement.
\item spectral-norm, calculate an eigenvalue using the power method.
\end{itemize}
